---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BFluxR

<!-- badges: start -->
<!-- badges: end -->

**Goals and Introduction**

BFluxR is a R interface to BFlux.jl which itself extends the famous Flux.jl machine learning library in Julia. BFlux is meant to make research and testing of Bayesian Neural Networks easy. It is not meant for production, but rather for explorations. Currently only regression problems are being kept in mind during the development, since those are the problems I am workin on. Extending things to classification problems should be rather straight forward though, since BFlux allows custom implementation of likelihoods and priors (at least in the Julia version). In the R version presented here, this is currently not possible. 

## Basics

BFluxR's and BFlux's are based on Flux.jl and thus take over a lot of their syntaxt. Before we demonstrate this, we first need to install and load BFluxR. Installation is currently only possible from Github: 

```{r}
# devtools::install_github("enweg/BFlurR")
```


## Variational Inference

## MCMC Methods

## Current Problems and Shortcomings

## References
